SKIN LESION CLASSIFICATION ON IMBALANCED DATA USING DEEP LEARNING WITH SOFT ATTENTION

### 2022-09-16 MDPI/sensors-1915564/template.tex
Paper Review 1.6

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Viet Dung Nguyen, Ngoc Dung Bui and Hoang Khoi Do}

@@

% Abstract (Do not insert blank lines, i.e. \\) s
\abstract{Today, the rapid development of industrial zones leads to an increased incidence of skin	diseases because of polluted air. According to a report by the American Cancer Society, it is estimated that in 2022 there will be about 100,000 people suffering from skin cancer and more than 7600 of these people will not survive. In the context that doctors at provincial hospitals and health facilities are overloaded, doctors at lower levels lack experience and having	a tool to support doctors in the process of diagnosing skin diseases quickly and accurately is essential. Along with the strong development of artificial intelligence technologies, many solutions to support the diagnosis of skin diseases have been researched and developed. In this paper, a combination of \add[H.K.D]{one} SOTA model \change[H.K.D]{such as}{including} DenseNet, InceptionNet, ResNet, NasNet,  MobileNet and Soft-Attention is proposed. Furthermore, personal information including age and gender are also used. It is worth to note that a new loss function	that takes into account the data imbalance is also proposed. Experimental results on data set HAM10000 show that using InceptionResNetV2 with Soft-Attention and new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and AUC scores of 0.81, 0.81, 0.82, and 0.99, respectively. Besides, using MobileNetV3Large combined with Soft-Attention and new loss function, even though the number of parameters is 11 times less, the number of hidden layers is 4 times less, it achieves 0.86 accuracy and 30 times faster diagnosis than InceptionResNetV2.}

@@

\section{Introduction} 
\subsection{Problem Statement}
\change[H.K.D]{One of the most common malignancies that cause death globally is skin cancer. In the United States, more than 9500 persons receive a skin cancer diagnosis each day \mbox{\cite{03358}}. The Skin Cancer Foundation reports that there is an ongoing rise in the incidence of skin cancer worldwide \mbox{\cite{11872}}. In the United States, 192,310 new cases of melanoma are anticipated to be detected in 2019. On the other hand, if patients receive an early diagnosis, their chances of survival are 99 percent. Survival is, however, generally poor after the illness has spread beyond the skin \mbox{\cite{11872}}. Additionally, there is a need for an efficient solution because to the rising prevalence of skin malignancies, low awareness among a population that is expanding, and a lack of sufficient clinical competence and services.}{Skin cancer is one of the most common cancers leading to worldwide death. Every day, more than 9500 \mbox{\cite{03358}} people in the United States are diagnosed with skin cancer. Otherwise, 3.6 \mbox{\cite{03358}} million people are diagnosed with basal cell skin cancer each year. According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase \mbox{\cite{11872}}. In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States \mbox{\cite{11872}}. On the other hand, if patients are early diagnosed, the survival rate is correlated with 99 percent. However, once the disease progresses beyond the skin, survival is poor \mbox{\cite{11872}}. Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solution.}

@@

\subsection{Related Works}
\change[H.K.D]{Skin lesion classification is not a new area, since there are many great performance models constructed. One of the most cutting-edge technologies that have been used is Soft-Attention as stated in \mbox{\cite{03358}}. Soumyyak et al construct several models formed by the combination of a backbone model including DenseNet201 \mbox{\cite{06993}}, InceptionResNetV2 \mbox{\cite{00567}}, ResNet50 \mbox{\cite{03385} \cite{05027}}, VGG16 \mbox{\cite{1556}} and Soft-Attention layer. Their approach is to add the Soft-Attention layer at the end or the middle of the backbone model. For ResNet50 and VGG16, the Soft-Attention layer is added after the third residual block and CNN block, respectively. DenseNet201 and InceptionResNetV2, otherwise concatenate with the Soft-Attention before a fully-connected layer, and then soft-max layer.

@@

On the other hand, skin lesion classification problems are not only applied by Deep Learning but also Machine Learning. Random Forest, XGBoost, and Support Vector Machines are tested by \mbox{\cite{03798}} of Rishu Garg et al. Besides, Isolation Forest is applied before the soft-max activation of the deep learning model to detect out of distribution skin lesion images as stated in \mbox{\cite{10348}} by Amirreza Rezvantalab et al. Matrix Transformation, besides is also applied before the soft-max activation function in \mbox{\cite{05045}} by Michele Alberti et al.}

@@

On the other hand, there are also many state of the art whose great performance on skin lesion classification. The Student and Teacher Model is also a high performance model in 2021 \mbox{\cite{03225}}, which is created by Xiaohan Xing et al as the combination of two model which share the memory with each other. Therefore, they can take full advantage of what others learn. The Student and Teacher model get the accuracy of 0.85, however the precision and f1-score are quite low 0.76.

@@

\subsubsection{Machine Learning Approach}
In Machine Learning, there are also many approaches. Since the image data is quite complex for Machine Learning algorithm, therefore using feature extractor or feature preprocessing to another form of data is recommended.

Random Forest, XGBoost, and Support Vector Machines are tested by \mbox{\cite{03798}} of Rishu Garg et al. In this approach, the data is fed directly into the Machine Learning algorithm and show out no promising result, therefore Rishu Garg et al dose not show the result of the Machine Learning algorithm.

@@

\subsection{Proposed Method}
In this research, a new model is constructed from the combination of:\\
- Backbone model including DenseNet201, InceptionResNetV2, ResNet50/152, NasNetLarge, NasNetMobile, and MobileNetV2/V3\\
- Using metadata including age, gender, localization as another input of the model\\
- Using Soft-Attention as a feature extractor of the model\\
- A new weight loss function
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}
\subsection{Materials}
\subsubsection{Image Data}
The data set used in this paper is the HAM10000 data set published by Havard University Dataverse \cite{10417}. There are total 7 classes in this data set containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), Basal cell Carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC). The distribution of the data set is shown in the Table \ref{table:data-distribution} below:

@@

\subsubsection{Metadata}
The HAM10000 data set \cite{10417} also contain the metadata of patient including gender, age, and the capturing position illustrated in Table \ref{table:metadata sample}
\begin{table}[H]
	\centering
	\begin{tabular}{|c c c c |} 
		\hline
		ID & Age & Gender & Local\\ 
		\hline
		ISIC-00001 & 15 & Male & back\\
		\hline
		ISIC-00002 & 85 & Female & elbow\\
		\hline
	\end{tabular}
	\caption{Metadata example in the data set}
	\label{table:metadata sample}
\end{table}
\subsection{Methodology}
\subsubsection{Overall Architecture}
The whole architecture of the model is represented in the Figure \ref{fig:main-model}. The model takes two input including Image data and Metadata. Metadata branch, otherwise is preprocessed before feeding into a dense layer then concatenate with the output of Soft-Attention layer.

@@

The Figure \ref{fig:model-structure} illustrates the overall structures of the combination of backbone models and Soft-Attention, which is used in this research. In detailed the combination of DenseNet201 and Soft-Attention is formed by replacing the three last DenseBlock, Global Average Pooling, and the fully-connected layer with the Soft-Attention Module. Similarity, ResNet50 and ResNet152 is also replaced the three last Residual Block, Global Average Pooling, and the fully connected layer with the Soft-Attention module. InceptionResNetV2, on the other hand, is replaced the Average Pool and the last Dropout with the Soft-Attention Module. Besides, the two last Normal Cell in NasNetLarge is replaced with the Soft-Attention module.

\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/Model Structure}
	\caption{Overall Original Model Architecture. This figure show the overall structure of the backbone model (non mobile-based model) including DenseNet201, InceptionResNetV2, ResNet50, ResNet152, and NasNetLarge. The detail structure and information can be found at the Apendix \ref{appendix-table:detailed structure model}}
	\label{fig:model-structure}
\end{figure}

The Figure \ref{fig:mobile-model-structure}, on the other hand shows the detailed structure of mobile-based mobile and its combination with Soft-Attention. All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution 1x1 by Soft-Attention module. The NasNetMobile, otherwise, combine with the Soft-Attention module by replacing the last Normal Cell. 
\begin{figure}[H]
	\centering
	\includegraphics[width=1\linewidth]{Definitions/Mobile Model Structure}
	\caption{Overall Mobile-based Model Architecture. This figure show the overall structure of the mobile-based backbone model including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile. The detail structure and information can be found at the Apendix \ref{appendix-table:detailed mobile model structure}}
	\label{fig:mobile-model-structure}
\end{figure}

\subsubsection{Input Schema}
\add[H.K.D]{Image preprocessing is an essential part before the training process because of the ability to extract main pattern of an image. In this stage, the image can be changed the color channel so that the main feature is separated from the useless part. Image Retrieval, otherwise has significantly create a vector that represent the main feature of an image. Those image retrieval techniques can be energy compaction, primitive pattern units, etc. Shervan Fekri-Ershad et al create an feature vector by calculating the element wise product of histogram vector in each channel of an image \mbox{\cite{2012.4305}}. Then comparing the Euclidean distance between this feature vector and the average feature vector of the whole data set with a thresh hold, they can extract the skin part of the image.}

In this research, the image data is both augmented for all class, the number of image increase to 18015 images and keep original form. Before feeding into the backbone model, the images is pre-processed by the input requirement of each model. DenseNet201 \cite{06993} require the input pixels values are scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet data set. In Resnet50 and Resnet152 \cite{03385} \cite{05027}, the images are converted from $RGB$ to $BGR$, then each color channel is zero-centered with respect to the ImageNet data set, without scaling. InceptionResNetV2\cite{11946}, on the other hand, will scale input pixels between $-1$ and $1$. Similarly, three versions of MobileNet \cite{04861} \cite{04381} \cite{02244}, NasNetMobile and NasNetLarge \cite{07012} require the input pixel is in range of $-1$ and $1$.

On the other hand, the metadata is also used as another input. In the research \cite{03910}, they decide to keep the missing value and set its value to $0$. The sex and anatomical site are categorical encoded. The age, on the other hand is numerical normalized. After processing, the metadata is fed into a two-layer neural network with 256 neurons each. Each layer contains batch normalization, a ReLU \cite{08375} activation, and dropout with $p = 0.4$. The network’s output is concatenated with the CNN’s feature vector after global average pooling. Especially, they use a simply data augmentation strategy to address the problem of missing values in metadata. During training, they randomly encode each property as missing with a probability of $p = 0.1$.

In this research, the unknowns is kept as a type as discussed in Metadata section. Sex, anatomical site and age are also category encoded and numerical normalized, respectively. After processing, the metadata is then concatenated and fed into a dense layer of 4096 neurons. Finally, this this dense layer is then concatenate with the output of Soft-Attention which is then discussed in Soft-Attention section. The Input schema is described in the Table \ref{fig:input-schema}

@@

\subsubsection{Backbone Model}
In this paper, the backbone models used in this paper are DenseNet201 \cite{06993}, Inception \cite{00567}, MobileNets \cite{04861} \cite{04381} \cite{02244}, ResNet \cite{03385} \cite{05027}, and NasNet \cite{07012}. The combination of DenseNet201, InceptionResNetV2 and Soft-Attention layer are both tested by the previous paper \cite{03358} with a great performance. Otherwise, Resnet50 also well classify but with much less number of parameter and depth than based on its f1-score and precision stated. Therefore, in this paper, the performance of the model Resnet152 and NasnetLarge which has the larger number of parameter and depth is analyzed. On the other hand, three version of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.

\begin{table}[H]
	\centering
	\begin{tabular}{|l | c c c|} 
		\hline
		Model & Size(MB) & Parameters & Depth \\ 
		\hline
		Resnet50 & 98 & 25.6M & 107 \\ 
		\hline
		Resnet152 & 232 & 60.4M & 311 \\ 
		\hline
		DenseNet201 & 80 & 20.2M & 402 \\
		\hline
		InceptionResNetV2 & 215 & 55.9M & 449 \\
		\hline
		MobileNet & 16 & 4.3M & 55 \\ 
		\hline
		MobileNetV2 & 14 & 3.5M & 105 \\ 
		\hline
		MobileNetV3Small & Unknown & 2.5M & 88 \\ 
		\hline
		MobileNetV3Large & Unknown & 5.5M & 118 \\
		\hline
		NasnetMobile & 23 & 5.3M & 308 \\
		\hline
		NasnetLarge & 343 & 88.9M & 533 \\ 
		\hline
	\end{tabular}
	\caption{Size and Parameters and Depth of backbone model used in this paper.}
	\label{table:model-summary}
\end{table}

\subsubsection{Soft-Attention Module}
Soft-Attention has been used in various applications: image caption generation such as \cite{03044} or handwriting verification \cite{202017}. Soft-Attention can ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights. Soft-Attention is described in the Equation \ref{eqn:softatt}.
\begin{equation}
	\label{eqn:softatt}
	f_{sa} = \gamma t\sum_{k=1}^{K}softmax(W_k * t)
\end{equation}

The Figure \ref{fig:soft-attention} shows the two main steps of applying Soft-Attention is applied in two main steps. Firstly, the input tensor is put in grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map \cite{08513}. This feature map called $t \in R^{h \times w \times d}$ where $h, w, \text{and } d$ is the shape of tensor generated by a Convolution Neural Network (CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$. The output of this convolution is normalized using the soft-max function to generate K (a constant value) attention maps. These $K$ attention maps are aggregated to produce a weight function called $\alpha$. This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, a learnable scalar. Finally, the output of Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps.

@@

After feeding into ReLU function layer, the heat feature map is processed in two paths. The first path is the 2-dimensional Max Pooling. In the second path, the feature map, on the other hand is fed into the Soft-Attention Layer before the 2-dimensional Max Pooling. After all, these two paths are then concatenated, fed into a ReLU layer, and a Dropout with the probability of $0.5$.

@@

where $\hat{y}^c_i$  is the output of model and $y^c_i$ is the target that the model should return, $W_c$ is the weight of class $c$. Since the data set face the imbalanced problem then class weight for the loss is applied. In this research, both of the original weight and a new weight formula is implementation. Originally, the weight is calculated by taking the inverse of percentage that each class accounts for. The new weight formula is described in the Equation \ref{eqn:weightformula} and \ref{eqn:vector-inverse-percent}. \add{This weight formula is the original weight multiplies with the inverse of number of class in the data set which make the training more balanced. It is inspired by the “balanced” heuristic proposed by Gary King et al\mbox{\cite{WV006-01}}}

@@

where $N$ is the number of training sample, $C$ is the number of class, $N_i$ is the number of sample in each class $i$. $D$ is the matrix contain the inverse of $C \times N_i$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{Experimental Setup}
\subsubsection{Training}
Before training, the data set is split into two sub set for training (90 percent) and validation (10 percent). Test set, otherwise is provided by the HAM10000 data set, contains 857 images. To analyze the effect of augmented data on the model, before the training the image data is augmented to $53573$ images by the following technique:\\
- Rotation Range: rotate the image in an \add[H.K.D]{angle range of 180}. \\
- Width and height shift range: Shift the image horizontally and vertically \add[H.K.D]{in a range of 0.1}, respectively. \\
- Zoom Range:  Zoom in or zoom out the image \add[H.K.D]{in a range of 0.1} to create new image. \\
- Horizontal and vertical flipping: Flipping the image horizontally and vertically to create new image.\\
Otherwise, all of models is trained with the Adam Optimizer \cite{6980} with the learning rate of $0.001$ which is reduced by a factor of $0.2$ to a minimum learning rate of $0.1 x 10^6$, and the epsilon is set to $0.1$. The initial epochs is set to 250 epochs and the Early Stopping is also applied to stop the training as the accuracy of validation set does not increase after $25$ epochs. Besides, the batch size is set to $32$.

>>>>

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Viet Dung Nguyen, Ngoc Dung Bui, and Hoang Khoi Do}

@@

% Abstract (Do not insert blank lines, i.e. \\) s
\abstract{Today, the rapid development of industrial zones leads to an increased incidence of skin	diseases because of polluted air. According to a report by the American Cancer Society, it is estimated that in 2022 there will be about 100,000 people suffering from skin cancer and more than 7600 of these people will not survive. In the context that doctors at provincial hospitals and health facilities are overloaded, doctors at lower levels lack experience, and having	a tool to support doctors in the process of diagnosing skin diseases quickly and accurately is essential. Along with the strong development of artificial intelligence technologies, many solutions to support the diagnosis of skin diseases have been researched and developed. In this paper, a combination of one Deep Learning model (DenseNet, InceptionNet, ResNet, etc) with Soft-Attention, which unsupervisedly extract a heat map of main skin lesions. Furthermore, personal information including age and gender is also used. It is worth noting that a new loss function that takes into account the data imbalance is also proposed. Experimental results on data set HAM10000 show that using InceptionResNetV2 with Soft-Attention and new loss function gives 90 percent accuracy, mean of precision, f1-score, recall-score, and AUC scores of 0.81, 0.81, 0.82, and 0.99, respectively. Besides, using MobileNetV3Large combined with Soft-Attention and new loss function, even though the number of parameters is 11 times less, the number of hidden layers is 4 times less, it achieves an accuracy of 0.86 and 30 times faster diagnosis than InceptionResNetV2.}

@@

	\section{Introduction} 
	\subsection{Problem Statement}
	\change[H.K.D]{One of the most common malignancies that cause death globally is skin cancer. In the United States, more than 9500 persons receive a skin cancer diagnosis each day \mbox{\cite{03358}}. The Skin Cancer Foundation reports that there is an ongoing rise in the incidence of skin cancer worldwide \mbox{\cite{11872}}. In the United States, 192,310 new cases of melanoma are anticipated to be detected in 2019. On the other hand, if patients receive an early diagnosis, their chances of survival are 99 percent. Survival is, however, generally poor after the illness has spread beyond the skin \mbox{\cite{11872}}. Additionally, there is a need for an efficient solution because of the rising prevalence of skin malignancies, low awareness among a population that is expanding, and a lack of sufficient clinical competence and services.}{Skin cancer is one of the most common cancers leading to worldwide death. Every day, more than 9500 \mbox{\cite{03358}} people in the United States are diagnosed with skin cancer. Otherwise, 3.6 \mbox{\cite{03358}} million people are diagnosed with basal cell skin cancer each year. According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase \mbox{\cite{11872}}. In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States \mbox{\cite{11872}}. On the other hand, if patients are early diagnosed, the survival rate is correlated with 99 percent. However, once the disease progresses beyond the skin, survival is poor \mbox{\cite{11872}}. Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solutions.}

@@

	\subsection{Related Works}
	\change[H.K.D]{Skin lesion classification is not a new area, since there are many great performance models constructed. One of the most cutting-edge technologies that have been used is Soft-Attention as stated in \mbox{\cite{03358}}. Soumyyak et al construct several models formed by the combination of a backbone model including DenseNet201 \mbox{\cite{06993}}, InceptionResNetV2 \mbox{\cite{00567}}, ResNet50 \mbox{\cite{03385} \cite{05027}}, VGG16 \mbox{\cite{1556}} and Soft-Attention layer. Their approach is to add the Soft-Attention layer at the end or the middle of the backbone model. For ResNet50 and VGG16, the Soft-Attention layer is added after the third residual block and CNN block, respectively. DenseNet201 and InceptionResNetV2, otherwise concatenate with the Soft-Attention before a fully-connected layer, and then the soft-max layer.

@@

		On the other hand, skin lesion classification problems are not only applied by Deep Learning but also Machine Learning. Random Forest, XGBoost, and Support Vector Machines are tested by \mbox{\cite{03798}} of Rishu Garg et al. Besides, Isolation Forest is applied before the soft-max activation of the deep learning model to detect out-of-distribution skin lesion images as stated in \mbox{\cite{10348}} by Amirreza Rezvantalab et al. Matrix Transformation, besides is also applied before the soft-max activation function in \mbox{\cite{05045}} by Michele Alberti et al.}

@@

		On the other hand, there are also many state-of-the-art whose great performance on skin lesion classification. The Student and Teacher Model is also a high-performance model in 2021 \mbox{\cite{03225}}, which is created by Xiaohan Xing et al as the combination of two models which share the memory with the other one. Therefore, they can take full advantage of what others learn. The Student and Teacher model gets an accuracy of 0.85, however, the precision and f1-score are quite low 0.76.

@@

		\subsubsection{Machine Learning Approach}
		In Machine Learning, there are also many approaches. Since the image data is quite complex for Machine Learning algorithms, therefore using feature extractor or feature preprocessing to another form of data is recommended.

		Random Forest, XGBoost, and Support Vector Machines are tested by \mbox{\cite{03798}} of Rishu Garg et al. In this approach, the data is fed directly into the Machine Learning algorithm and shows no promising result, therefore Rishu Garg et al does not show the result of the Machine Learning algorithm.

@@

	\subsection{Proposed Method}
	In this research, a new model is constructed from the combination of:\\
	- Backbone model including DenseNet201, InceptionResNetV2, ResNet50/152, NasNetLarge, NasNetMobile, and MobileNetV2/V3\\
	- Using metadata including age, gender, and localization as another input of the model\\
	- Using Soft-Attention as a feature extractor of the model\\
	- A new weight loss function
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Materials and Methods}
	\subsection{Materials}
	\subsubsection{Image Data}
	The data set used in this paper is the HAM10000 data set published by Havard University Dataverse \cite{10417}. There are total 7 classes in this data set containing Actinic keratoses and intraepithelial carcinoma or Bowen's disease (AKIEC), Basal cell Carcinoma (BCC),  benign keratosis-like lesions (solar lentigines / seborrheic keratoses andchen-planus like keratoses, BKL), dermatofibroma (DF), melanoma (MEL), melanocytic nevi (NV), and vascular lesions (angiomas, angiokeratomas, pyogenic granulomas and hemorrhage, VASC). The distribution of the data set is shown in Table \ref{table:data-distribution} below:

@@

	\subsubsection{Metadata}
	The HAM10000 data set \cite{10417} also contains the metadata of the patient including gender, age, and the capturing position illustrated in Table \ref{table:metadata sample}
	\begin{table}[H]
		\centering
		\begin{tabular}{|c c c c |} 
			\hline
			ID & Age & Gender & Local\\ 
			\hline
			ISIC-00001 & 15 & Male & back\\
			\hline
			ISIC-00002 & 85 & Female & elbow\\
			\hline
		\end{tabular}
		\caption{Metadata example in the data set}
		\label{table:metadata sample}
	\end{table}
	\subsection{Methodology}
	\subsubsection{Overall Architecture}
	The whole architecture of the model is represented in Figure \ref{fig:main-model}. The model takes two inputs including Image Data and Metadata. The metadata branch otherwise is preprocessed before feeding into a dense layer and then concatenate with the output of the Soft-Attention layer.

@@

	Figure \ref{fig:model-structure} illustrates the overall structures of the combination of backbone models and Soft-Attention, which is used in this research. In detail, the combination of DenseNet201 and Soft-Attention is formed by replacing the three last DenseBlock, Global Average Pooling, and the fully-connected layer with the Soft-Attention Module. Similarly, ResNet50 and ResNet152 also replaced the three last Residual Block, Global Average Pooling, and the fully connected layer with the Soft-Attention module. InceptionResNetV2, on the other hand, is replaced the Average Pool and the last Dropout with the Soft-Attention Module. Besides, the two last Normal Cell in NasNetLarge is replaced with the Soft-Attention module.

	\begin{figure}[H]
		\centering
		\includegraphics[width=1\linewidth]{Definitions/Model Structure}
		\caption{Overall Original Model Architecture. This figure show the overall structure of the backbone model (non mobile-based model) including DenseNet201, InceptionResNetV2, ResNet50, ResNet152, and NasNetLarge. The detailed structure and information can be found in the Appendix \ref{appendix-table:detailed structure model}}
		\label{fig:model-structure}
	\end{figure}

	Figure \ref{fig:mobile-model-structure}, on the other hand, shows the detailed structure of mobile-based mobile and its combination with Soft-Attention. All of the MobileNet versions combine with the Soft-Attention module by replacing the two last convolution 1x1 with the Soft-Attention module. The NasNetMobile, otherwise, combines with the Soft-Attention module by replacing the last Normal Cell. 
	\begin{figure}[H]
		\centering
		\includegraphics[width=1\linewidth]{Definitions/Mobile Model Structure}
		\caption{Overall Mobile-based Model Architecture. This figure shows the overall structure of the mobile-based backbone model including MobileNetV2, MobileNetV3Small, MobileNetV3Large, and NasNetMobile. The detailed structure and information can be found in the Appendix \ref{appendix-table:detailed mobile model structure}}
		\label{fig:mobile-model-structure}
	\end{figure}

	\subsubsection{Input Schema}
	\add[H.K.D]{Image preprocessing is an essential part of the training process because of the ability to extract the main pattern of an image. In this stage, the image can be changed to the other color channel so that the main feature is separated from the useless part. Image Retrieval otherwise has significantly created a vector that represents the main feature of an image. Those image retrieval techniques can be energy compaction, primitive pattern units, etc. Shervan Fekri-Ershad et al create a feature vector by calculating the element-wise product of the histogram vector in each channel of an image \mbox{\cite{2012.4305}}. Then comparing the Euclidean distance between this feature vector and the average feature vector of the whole data set with a thresh hold, they can extract the skin part of the image.}

	In this research, the image data is augmented for all class, the number of image increase to 18015 images and keep the original form. Before feeding into the backbone model, the images are pre-processed by the input requirement of each model. DenseNet201 \cite{06993} requires the input pixel values to be scaled between $0$ and $1$ and each channel is normalized with respect to the ImageNet data set. In Resnet50 and Resnet152 \cite{03385} \cite{05027}, the images are converted from $RGB$ to $BGR$, then each color channel is zero-centered with respect to the ImageNet data set, without scaling. InceptionResNetV2\cite{11946}, on the other hand, will scale input pixels between $-1$ and $1$. Similarly, three versions of MobileNet \cite{04861} \cite{04381} \cite{02244}, NasNetMobile and NasNetLarge \cite{07012} require the input pixel is in range of $-1$ and $1$.

	On the other hand, the metadata is also used as another input. In the research \cite{03910}, they decide to keep the missing value and set its value to $0$. The sex and anatomical site are categorically encoded. The age, on the other hand, is numerically normalized. After processing, the metadata is fed into a two-layer neural network with 256 neurons each. Each layer contains batch normalization, a ReLU \cite{08375} activation, and dropout with $p = 0.4$. The network’s output is concatenated with the CNN’s feature vector after global average pooling. Especially, they use a simple data augmentation strategy to address the problem of missing values in metadata. During training, they randomly encode each property as missing with a probability of $p = 0.1$.

	In this research, the unknowns are kept as a type as discussed in the Metadata section. Sex, anatomical site, and age are also category encoded and numerically normalized, respectively. After processing, the metadata is then concatenated and fed into a dense layer of 4096 neurons. Finally, this dense layer is then concatenated with the output of Soft-Attention which is then discussed in the Soft-Attention section. The Input schema is described in Table \ref{fig:input-schema}

@@

	\subsubsection{Backbone Model}
	In this paper, the backbone models used in this paper are DenseNet201 \cite{06993}, Inception \cite{00567}, MobileNets \cite{04861} \cite{04381} \cite{02244}, ResNet \cite{03385} \cite{05027}, and NasNet \cite{07012}. The combination of DenseNet201, InceptionResNetV2, and Soft-Attention layer are both tested by the previous paper \cite{03358} with a great performance. Otherwise, Resnet50 also well classify but with a much less number of parameters and depth than based on its f1-score and precision stated. Therefore, in this paper, the performance of the model Resnet152 and NasnetLarge which has the larger number of parameter and depth is analyzed. On the other hand, three versions of MobileNet and the NasnetMobile will also be analyzed which has a small number of parameter and depth.

	\begin{table}[H]
		\centering
		\begin{tabular}{|l | c c c|} 
			\hline
			Model & Size(MB) & No. Trainable Parameters & Depth \\ 
			\hline
			Resnet50 & 98 & 25,583,592 & 107 \\ 
			\hline
			Resnet152 & 232 & 60,268,520 & 311 \\ 
			\hline
			DenseNet201 & 80 & 20,013,928 & 402 \\
			\hline
			InceptionResNetV2 & 215 & 55,813,192 & 449 \\
			\hline
			MobileNetV2 & 14 & 3,504,872 & 105 \\ 
			\hline
			MobileNetV3Small & Unknown & 2,542,856 & 88 \\ 
			\hline
			MobileNetV3Large & Unknown & 5,483,032 & 118 \\
			\hline
			NasnetMobile & 23 & 5,289,978 & 308 \\
			\hline
			NasnetLarge & 343 & 88,753,150 & 533 \\ 
			\hline
		\end{tabular}
		\caption{Size and Parameters and Depth of backbone model used in this paper.}
		\label{table:model-summary}
	\end{table}

	\subsubsection{Soft-Attention Module}
	Soft-Attention has been used in various applications: image caption generation such as \cite{03044} or handwriting verification \cite{202017}. Soft-Attention can ignore irrelevant areas of the image by multiplying the corresponding feature maps with low weights. Soft-Attention is described in Equation \ref{eqn:softatt}.
	\begin{equation}
		\label{eqn:softatt}
		f_{sa} = \gamma t\sum_{k=1}^{K}softmax(W_k * t)
	\end{equation}

	Figure \ref{fig:soft-attention} shows the two main steps of applying Soft-Attention. Firstly, the input tensor is put in grid-based feature extraction from the high-resolution image, where each grid cell is analyzed in the whole slide to generate a feature map \cite{08513}. This feature map called $t \in R^{h \times w \times d}$ where $h, w, \text{and } d$ is the shape of tensor generated by a Convolution Neural Network (CNN), is then input to a 3D convolution layer whose weights is $W_k \in R^{h \times w \times d \times K}$. The output of this convolution is normalized using the soft-max function to generate K (a constant value) attention maps. These $K$ attention maps are aggregated to produce a weight function called $\alpha$. This $\alpha$ function is then multiplied with feature tensor $t$ and scaled by $\gamma$, a learnable scalar. Finally, the output of the Soft-Attention function $f_{sa}$ is the concatenation of the beginning feature tensor $t$ and the scaled attention maps.

@@

	After feeding into the ReLU function layer, the heat feature map is processed in two paths. The first path is the 2-dimensional Max Pooling. In the second path, the feature map, on the other hand, is fed into the Soft-Attention Layer before the 2-dimensional Max Pooling. After all, these two paths are then concatenated, fed into a ReLU layer, and a Dropout with the probability of $0.5$.

@@

	where $\hat{y}^c_i$  is the output of the model and $y^c_i$ is the target that the model should return, $W_c$ is the weight of class $c$. Since the data set face the imbalanced problem then class weight for the loss is applied. In this research, both the original weight and a new weight formula are implemented. Originally, the weight is calculated by taking the inverse of the percentage that each class accounts for. The new weight formula is described in the Equation \ref{eqn:weightformula} and \ref{eqn:vector-inverse-percent}. \add{This weight formula is the original weight multiplied by the inverse of the number of classes in the data set which makes the training more balanced. It is inspired by the “balanced” heuristic proposed by Gary King et al\mbox{\cite{WV006-01}}}

@@

	where $N$ is the number of the training sample, $C$ is the number of classes, and $N_i$ is the number of samples in each class $i$. $D$ is the matrix containing the inverse of $C \times N_i$.

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Results}
	\subsection{Experimental Setup}
	\subsubsection{Training}
	Before training, the data set is split into two subsets for training (90 percent) and validation (10 percent). The test set, otherwise provided by the HAM10000 data set, contains 857 images. To analyze the effect of augmented data on the model, before the training the image data is augmented to $53573$ images by the following technique:\\
	- Rotation Range: rotate the image in an \add[H.K.D]{angle range of 180}. \\
	- Width and height shift range: Shift the image horizontally and vertically \add[H.K.D]{in a range of 0.1}, respectively. \\
	- Zoom Range:  Zoom in or zoom out the image \add[H.K.D]{in a range of 0.1} to create new image. \\
	- Horizontal and vertical flipping: Flipping the image horizontally and vertically to create a new image.\\
	Otherwise, all models are trained with the Adam Optimizer \cite{6980} with the learning rate of $0.001$ which is reduced by a factor of $0.2$ to a minimum learning rate of $0.1 x 10^6$, and the epsilon is set to $0.1$. The initial epochs are set to 250 epochs and the Early Stopping is also applied to stop the training as the accuracy of the validation set does not increase after $25$ epochs. Besides, the batch size is set to $32$.

	\subsubsection{Tools}
	TensorFlow and Keras are two of the most popular framework to build a deep learning model. In this research, Keras based on TensorFlow is used to build, and clone the backbone model which is pre-trained with the image-net data set. Otherwise, the models are trained by NVIDIA RTX TitanV, and the data set is pre-processed with the CPU Intel I5 32 processors, and RAM 32GB. In detail, the GPU is set up with CUDA 11.6, cuDNN 8.3, and ChipSRT as the requirement of TensorFlow version 2.7.0.
	\subsubsection{Evaluation Metrics}
	\begin{figure}[!htb]
		\begin{minipage}{0.48\textwidth}
			\centering
			\includegraphics[width=1.1\linewidth]{Definitions/Confusion-matrix}
			\caption{Confusion Matrix}\label{fig:confusion-matrix}
		\end{minipage}\hfill
		\begin{minipage}{0.48\textwidth}
			\centering
			\includegraphics[width=.7\linewidth]{Definitions/AUC}
			\caption{Area Under the Curve}\label{fig:AUC}
		\end{minipage}
	\end{figure}
	The model is evaluated by using the confusion matrix and related metrics. The Figure \ref{fig:confusion-matrix} illustrates the presentation of a $2 \times 2$ confusion matrix used for $2$ class. Consider a confusion matrix $A$ with $C$ number of class. Let $A^i$ and $A^j$ be the set of $A$ rows and columns respectively, therefore $A^i_k$ is the element at row i and column k
	\[
	A = \begin{bmatrix}
		a_{11} & a_{12} & \dots & a_{1j} \\
		a_{21} & a_{22} & \dots & a_{2j} \\
		\vdots & \vdots	&  & \vdots\\
		a_{i1} & a_{i2} & \dots & a_{ij} 
	\end{bmatrix}
	\]
	The True Positive(TP) of all classes in this case is the main diagonal of the matrix $A$. The following method is used to calculate the False Positives(FP), False Negatives(FN), and True Negatives(TN) of all classes:
